Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-08-30 ms.tex
went through the difference between this and the originally submitted paper to check if there was anything I forgot to put in boldface. Only found 1 word like this that was bovious.

We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral \textbf{types} L4-L5: {\sha} and {\shb}.
These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
We find that {\sha} has marginal variability and no significant wavelength dependence; while
{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which declines toward the near infrared (2.4$~\mu$m).
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
\textbf{\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.}

>>>>

We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral \textbf{types} L4-L5: {\sha} and {\shb}.
These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
We find that {\sha} has marginal variability and no significant wavelength dependence; while
{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m), which declines \textbf{toward} the near infrared (2.4$~\mu$m).
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
\textbf{\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.}
